\documentclass[a4paper, 12pt] {article}
\usepackage{xcolor, soul}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{epsfig}
 \usepackage{url}

\setlength{\textwidth}{6.5in} \setlength{\textheight}{8.5in}
\setlength{\evensidemargin}{0in} \setlength{\oddsidemargin}{0in}
\setlength{\topmargin}{0in}

\setlength{\parindent}{0pt} \setlength{\parskip}{0.1in}

% 1.5 line-spaced document.
\renewcommand{\baselinestretch}{1.2}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}


\newcommand{\lyxaddress}[1]{
  \par {\raggedright #1
  \vspace{0.4em}
  \noindent\par}
}
\begin{document}
\begin {center}

\LARGE{\textbf{Manuscript ID:}\\
\large{\textbf{(Answers to Referee's Recommendations)}}}

\end {center}

\vspace {8 mm}

\small {We would first like to thank the reviewers for their
valuable comments, which helped us in improving the paper at several
places. We took each comment into consideration and did the
necessary modifications in the revised version. In this document, 
we
include pointers (as Section, Page and line(s) number(s)) to the modifications in the modified version of paper PDF  in response to the comments for easy traceability. }\\



%
%
%
%\newpage
\section{Referee's Recommendations}

\subsection{Reviewer 1}
\begin{itemize}
  
\item \emph{Isabelle/Solidity has also been the focus of the recent work in \cite{try}, which provided more details for the verification framework. The paper could cite this work and clarify its contribution/content on top of \cite{try} (e.g., offering a practical, user-friendly tool for verification).
}


\textbf{Reply:} Introduced and clarify the contributions in Introduction section (Page 1, Lines 39-42) and also reference is added in the Related Work section (Page 7, Lines 190-193).

\end{itemize}


\newpage
\subsection{Reviewer 2}
\begin{itemize}
	\item \emph{There are at least two earlier publications by the same authors regarding Isabelle/Solidity ("Secure Smart Contracts with Isabelle/Solidity", 2024, and "Isabelle/Solidity, a deep embedding", 2025), and a third about a related but distinct semantics for Solidity, also with Isabelle ("A Denotational Semantics of Solidity in Isabelle/HOL", 2021). }
	
	
	\textbf{Reply:} Introduced and clarify the contributions in Introduction section (Page 1, Lines 39-42) and also reference is added in the Related Work section (Page 7, Lines 190-193).
	
	\item \emph{several titles in the reference section are written in all-lowercase }
	
	
	\textbf{Reply:} Fixed
	
  \item \emph{some instances of "proof" instead of "prove" (e.g line 150) }


\textbf{Reply:} Fixed


\item \emph{ the invariant of the case study is given as example 5.1 in a box, breaking the flow of the text, although it is integrally part of of the main text and referred in the listing 4 afterwards, which is not part of the example 
}

\textbf{Reply:}  Fixed, Verification section (Page 5, Lines 147-154)

\end{itemize}

\newpage
\subsection{Reviewer 3}
\begin{itemize}
	\item \emph{The specification of the example is slightly confusing because while a secret number is generated, only the mod 2 of that number is relevant, modeled as HEADS and TAILS. I might have missed something but why not have a secret Boolean instead of a secret number?  }
	
	
	\textbf{Reply:} Explained the reason for using secrete number rather bool in Case Study Section (Page 3, Lines 104-108).
	
	\item \emph{Page 4 mentions that "What follows is a specification of stack (param), memory (memory), and calldata (calldata) parameters and corresponding types." I didn't get where these three components were described. Could that be clarified?  }
	
	
	\textbf{Reply:} Added Table 1 in Section 2 (Isabelle/Solidity, Page 2, Line 69) to explain the different types of stores in Solidity and their properties.
	
  \item \emph{Page 5 mentions that "The postconditions require a method to update the corresponding state of the lle game properly." I'm not sure I understood that point. Are you saying that for example "decideBet\_post" is a postcondition that requires "decideBet" from listing 2 to update its state appropriately? Could this be explained in more detail? For example by providing (part of) "decideBet\_post" and explaining how it requires "decideBet" to update its state? "decideBet\_post" seems to be presented in listing 5, but this is not explicitly said. The name of the listing could potentially mention "decideBet\_post". Also, what's K in figure 4? }


\textbf{Reply:} Isabelle/HOL definition of Post-condition (PlaceBet\_post) has been included and explained in Verification section (Page 6, Lines 162-164).


\item \emph{ typo line 59: "programms"
}

\textbf{Reply:}  Fixed

\item \emph{ typo line 66: "requires a them" }\\
\textbf{Reply:}  Fixed
 
 \item \emph{typo line 102: "is in not in"  }\\
\textbf{Reply:}  Fixed
 
  \item \emph{typo line 150: "tries to proof"  }\\
\textbf{Reply:}  Fixed
\end{itemize}


%
%
\bibliographystyle{plain}
\bibliography{comments}

\end{document}
